Vision and Cognitive Systems Final Project

### 2020-06-30 Paper_Presentation/paper/paper.tex
3d model figures added
hyperref

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{csvsimple}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

A little problem has arisen due to the high number of paintings representing persons, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../screenshots_3d_model/screenshot_01.jpg}}
\caption{3dmodel}
\label{fig_3d_model}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../screenshots_3d_model/screenshot_03.png}}
\caption{3d model 2}
\label{fig_3d_model_2}
\end{figure}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{csvsimple}
\usepackage{hyperref}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

A little problem has arisen due to the high number of paintings representing persons as show in figure \ref{fig_People_detection_error}, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../3DModel/collage_06.jpg}}
\caption{Original image vs Superimposed image}
\label{fig_3d_model}
\end{figure}
